Interval Probability for Fuzzy Quantum Theories

### 2016-06-24 prob.tex
prob.tex Global replace E by P for projection~~

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the
  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
  consider variants constructed over finite
  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probability measures~\cite{PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1983,Mermin2007} and the map is given by:
  $E \mapsto \ip{\psi}{E\psi}$.
\item given a probability measure $\mu$
  mapping each event $E$
  to a probability, is there a \emph{unique} state $\psi$
  such that $\mu(E)
  =
  \ip{\psi}{E\psi}$? In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

For a given set of events $\events$, there are many possible probability
measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
a postulate of quantum mechanics, states that each pure quantum state
$\ket{\phi}$ induces a probability measure $\mu^B_{\phi}$
as follows: 
\[
\mu^B_{\phi}(E)=\ip{\phi}{E\phi}
\]

Moreover, the Born rule can be extended to a mixed state. Suppose
we want to prepare a quantum system. As we discussed in classical
probability, our ability of preparing a state might not be prefect.
If we want to prepare $\ket{\phi}$, we may turn out preparing a set
of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$. Then,
the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
measure introduced by $\rho$ is the combination of $\mu^B_{\phi_{j}}$
with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
\begin{eqnarray}
\mu^B_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\phi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

@@

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\mu^B_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a quantum probability measure. Because $\mu$ is almost
the same as a quantum probability measure~$\mu^B_{\ket{0}}$, we only
need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\mu^B_{\rho}(E)=1$ if and only if $\rho$ represents
a pure state and $\rho=E$. \qed\end{example}

@@

When we pick $\mathscr{I}=\left\{ \left[x,x\right]\middle|x\in\left[0,1\right]\right\} $,
for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
we can define a corresponding quantum \emph{$\mathscr{I}$}-interval-valued
probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}\left(E\right)=\left[\mu\left(E\right),\mu\left(E\right)\right]$.
In this sense, every usual quantum probability measure can be considered
as a quantum interval-valued probability measure. There are more interesting
examples as we now show.

\begin{example}[Quantum three-value interval-valued probability
measure] We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs~and \necess~as before,
and \emph{$\left[0,1\right]$} is called \unknown~because it provides
no information. For any Hilbert space and any quantum probability
measure~$\mu:\events\rightarrow\left[0,1\right]$,
we can define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by 
\[
\bar{\mu}(E)=\iota\left(\mu(E)\right)\textrm{ ,}
\]
where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{, if }x=1\textrm{ ;}\\
\imposs & \textrm{, if }x=0\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
$\iota$ has two interesting properties 
\begin{eqnarray*}
\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right) & = & 1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)\\
\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right) & \subseteq & \sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)\textrm{ ,}
\end{eqnarray*}
where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
By applying these two properties, it is easy to verify $\bar{\mu}$
is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}

@@

\begin{example}[One-qubit quantum interval-valued probability measure]
Given a two dimensional Hilbert space, a vector $\ket{\psi}$ can
be normalized and written in $\left(\begin{array}{c}
\cos\theta\\
\rme^{\rmi\gamma}\sin\theta
\end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma\le2\pi$. Consider
a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
defined by 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1}) & = & \necess\textrm{ ,}\\
\bar{\mu}(\proj{\psi}) & = & \begin{cases}
\necess & \textrm{, if }\theta=0\textrm{ ;}\\
\likely & \textrm{, if }0<\theta<\frac{\pi}{4}\textrm{ ;}\\
\likely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }0\le\gamma<\pi\textrm{ ;}\\
\unlikely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }\pi\le\gamma<2\pi\textrm{ ;}\\
\unlikely & \textrm{, if }\frac{\pi}{4}<\theta<\frac{\pi}{2}\textrm{ ;}\\
\imposs & \textrm{, if }\theta=\frac{\pi}{2}\textrm{ .}
\end{cases}
\end{eqnarray*}
Let $\ket{\psi^{\perp}}$ be the state perpendicular to $\ket{\psi}$.
Then, the vector representation of $\ket{\psi^{\perp}}$ can be simplified
as 
\[
\left(\begin{array}{c}
-\rme^{\rmi\gamma}\sin\theta\\
\cos\theta
\end{array}\right)=-\rme^{\rmi\gamma}\left(\begin{array}{c}
\cos\left(\frac{\pi}{2}-\theta\right)\\
\rme^{\rmi\left(\pi-\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)
\end{array}\right)
\]
so we have
\[
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi}\right)=\bar{\mu}\left(\proj{\psi^{\perp}}\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(\proj{\psi}\right)\textrm{ .}
\]
Hence, $\bar{\mu}$ is a quantum $\mathscr{I}$-interval-valued
probability measure. Notice that for all projection~$E$, $\mu^B_{\ket{0}}(E)\in\bar{\mu}(E)$
implies that $\bar{\mu}(E)$ is one of quantum
$\mathscr{I}$-interval-valued probability measures corresponding
to $\mu^B_{\ket{0}}(E)$. However,
$\mu^B_{\ket{0}}(E)$ can correspond
to infinity many quantum $\mathscr{I}$-interval-valued probability
measures by twisting the definition involving $\gamma$.\qed\end{example}

@@

Although it seems that we need an infinite long table to specify the
quantum probability measure~$\mu$, our $\mu$ is actually
given by a simple formula~$\melement{0}{E}$. In general, Born discovered
each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu^B_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1983,Mermin2007}:
\begin{equation}
\mu^B_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
The Born rule satisfies the following properties:
\begin{itemize}
\item It can be extend to mixed states. Given a mixed state represented
by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
the Born rule can be extended to $\rho$ by 
\begin{eqnarray}
\mu^B_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}
Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
is a classical probability space. Therefore, when we discretize the
Hilbert space later, we may need to discretize this probability space
as well.
\item $\mu^B_{\rho}$ is a probability measure for all mixed state~$\rho$.
\item $\ip{\psi}{\phi}=0\Leftrightarrow\mu^B_{\psi}\left(\proj{\phi}\right)=0$.
\item $\mu^B_{\psi}\left(E\right)=\mu^B_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}

@@

Fix a pure normalized state $\phi$, $\mu'^B_{\phi}$ is a quantum
probability measure by condition 2. By Gleason's theorem, there is
a mixed state ~$\rho'$, such that $\mu'^B_{\phi}\left(E\right)=\Tr\left(\rho'E\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(E\right)$
for all event $E$.

Consider the event $E'=\mathbb{1}-\proj{\phi}$, we have 
\begin{eqnarray*}
0 & \overset{\textrm{Condition 3}}{=} & \mu^B_{\phi}\left(E'\right)\\
 & = & \sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(E'\right)
\end{eqnarray*}
Because $q_{j}>0$, we have $\mu^B_{\psi_{j}}\left(E\right)=0$,
i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $E'$.
However, the only subspace orthogonal to $E'$ is span by $\ket{\phi}$.
Hence, $\mu'^B_{\phi}=\mu^B_{\phi}$.
\end{proof}

@@

However, there is a $\mathscr{L}_{2}$-valued probability measure
\[
\hat{\mu}_{1}\left(E\right)=\begin{cases}
\imposs & \textrm{, if }E=\proj{+};\\
\bar{\mu}(E) & \textrm{, otherwise.}
\end{cases}
\]
such that $\hat{\mu}_{1}\ne\bar{\mu}_{\psi}$ for all mixed state
$\ket{\psi}$.

>>>>

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the
  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
  consider variants constructed over finite
  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probability measures~\cite{PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1983,Mermin2007} and the map is given by:
  $P \mapsto \ip{\psi}{P\psi}$.
\item given a probability measure $\mu$
  mapping each event $P$
  to a probability, is there a \emph{unique} state $\psi$
  such that $\mu(P)
  =
  \ip{\psi}{P\psi}$? In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

For a given set of events $\events$, there are many possible probability
measures $\mu:\events\rightarrow[0,1]$. The Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007},
a postulate of quantum mechanics, states that each pure quantum state
$\ket{\phi}$ induces a probability measure $\mu^B_{\phi}$
as follows: 
\[
\mu^B_{\phi}(P)=\ip{\phi}{P\phi}
\]

Moreover, the Born rule can be extended to a mixed state. Suppose
we want to prepare a quantum system. As we discussed in classical
probability, our ability of preparing a state might not be prefect.
If we want to prepare $\ket{\phi}$, we may turn out preparing a set
of state~$\ket{\phi_{j}}$ each with probability~$q_{j}$. Then,
the state of the system can be expressed as a density matrix~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$,
where $\sum_{j}q_{j}=1$. It is natural that the quantum probability
measure introduced by $\rho$ is the combination of $\mu^B_{\phi_{j}}$
with respect to probability $q_{j}$~\cite{peres1995quantum,544199,RiederSvozil2007}:
\begin{eqnarray}
\mu^B_{\rho}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\phi_{j}}\left(P\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}

@@

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(P)=\begin{cases}
1 & \textrm{, if }P=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }P=\proj{\ms}\textrm{ ;}\\
\mu^B_{\ket{0}}(P) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a quantum probability measure. Because $\mu$ is almost
the same as a quantum probability measure~$\mu^B_{\ket{0}}$, we only
need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\mu^B_{\rho}(P)=1$ if and only if $\rho$ represents
a pure state and $\rho=P$. \qed\end{example}

@@

When we pick $\mathscr{I}=\left\{ \left[x,x\right]\middle|x\in\left[0,1\right]\right\} $,
for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
we can define a corresponding quantum \emph{$\mathscr{I}$}-interval-valued
probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}\left(P\right)=\left[\mu\left(P\right),\mu\left(P\right)\right]$.
In this sense, every usual quantum probability measure can be considered
as a quantum interval-valued probability measure. There are more interesting
examples as we now show.

\begin{example}[Quantum three-value interval-valued probability
measure] We consider three intervals\emph{ }$\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$
and $\left[1,1\right]$ are called \imposs~and \necess~as before,
and \emph{$\left[0,1\right]$} is called \unknown~because it provides
no information. For any Hilbert space and any quantum probability
measure~$\mu:\events\rightarrow\left[0,1\right]$,
we can define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by 
\[
\bar{\mu}(P)=\iota\left(\mu(P)\right)\textrm{ ,}
\]
where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{, if }x=1\textrm{ ;}\\
\imposs & \textrm{, if }x=0\textrm{ ;}\\
\unknown & \textrm{, otherwise.}
\end{cases}
\]
$\iota$ has two interesting properties 
\begin{eqnarray*}
\iota\left(\mathbb{1}\tensor*[_{\mathbb{R}}]{-}{}x\right) & = & 1\tensor*[_{\mathscr{I}}]{-}{}\iota\left(x\right)\\
\iota\left(\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\right) & \subseteq & \sideset{_{\mathscr{I}}}{_{i}}\sum\iota\left(x_{i}\right)\textrm{ ,}
\end{eqnarray*}
where $x$ and $\sideset{_{\mathbb{R}}}{_{i}}\sum x_{i}\in\left[0,1\right]$.
By applying these two properties, it is easy to verify $\bar{\mu}$
is a quantum \emph{$\mathscr{I}$}-interval-valued probability measure.\qed\end{example}

@@

\begin{example}[One-qubit quantum interval-valued probability measure]
Given a two dimensional Hilbert space, a vector $\ket{\psi}$ can
be normalized and written in $\left(\begin{array}{c}
\cos\theta\\
\rme^{\rmi\gamma}\sin\theta
\end{array}\right)$, where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma\le2\pi$. Consider
a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
defined by 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1}) & = & \necess\textrm{ ,}\\
\bar{\mu}(\proj{\psi}) & = & \begin{cases}
\necess & \textrm{, if }\theta=0\textrm{ ;}\\
\likely & \textrm{, if }0<\theta<\frac{\pi}{4}\textrm{ ;}\\
\likely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }0\le\gamma<\pi\textrm{ ;}\\
\unlikely & \textrm{, if }\theta=\frac{\pi}{4}\textrm{ and }\pi\le\gamma<2\pi\textrm{ ;}\\
\unlikely & \textrm{, if }\frac{\pi}{4}<\theta<\frac{\pi}{2}\textrm{ ;}\\
\imposs & \textrm{, if }\theta=\frac{\pi}{2}\textrm{ .}
\end{cases}
\end{eqnarray*}
Let $\ket{\psi^{\perp}}$ be the state perpendicular to $\ket{\psi}$.
Then, the vector representation of $\ket{\psi^{\perp}}$ can be simplified
as 
\[
\left(\begin{array}{c}
-\rme^{\rmi\gamma}\sin\theta\\
\cos\theta
\end{array}\right)=-\rme^{\rmi\gamma}\left(\begin{array}{c}
\cos\left(\frac{\pi}{2}-\theta\right)\\
\rme^{\rmi\left(\pi-\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)
\end{array}\right)
\]
so we have
\[
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi}\right)=\bar{\mu}\left(\proj{\psi^{\perp}}\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(\proj{\psi}\right)\textrm{ .}
\]
Hence, $\bar{\mu}$ is a quantum $\mathscr{I}$-interval-valued
probability measure. Notice that for all projection~$P$, $\mu^B_{\ket{0}}(P)\in\bar{\mu}(P)$
implies that $\bar{\mu}(P)$ is one of quantum
$\mathscr{I}$-interval-valued probability measures corresponding
to $\mu^B_{\ket{0}}(P)$. However,
$\mu^B_{\ket{0}}(P)$ can correspond
to infinity many quantum $\mathscr{I}$-interval-valued probability
measures by twisting the definition involving $\gamma$.\qed\end{example}

@@

Although it seems that we need an infinite long table to specify the
quantum probability measure~$\mu$, our $\mu$ is actually
given by a simple formula~$\melement{0}{P}$. In general, Born discovered
each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu^B_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $P\in\qevents$ as follows~\cite{Born1983,Mermin2007}:
\begin{equation}
\mu^B_{\psi}(P)=\frac{\melement{\psi}{P}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
The Born rule satisfies the following properties:
\begin{itemize}
\item It can be extend to mixed states. Given a mixed state represented
by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
the Born rule can be extended to $\rho$ by 
\begin{eqnarray}
\mu^B_{\rho}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\Psi_{j}}\left(P\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}
Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
is a classical probability space. Therefore, when we discretize the
Hilbert space later, we may need to discretize this probability space
as well.
\item $\mu^B_{\rho}$ is a probability measure for all mixed state~$\rho$.
\item $\ip{\psi}{\phi}=0\Leftrightarrow\mu^B_{\psi}\left(\proj{\phi}\right)=0$.
\item $\mu^B_{\psi}\left(P\right)=\mu^B_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}P\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}

@@

Fix a pure normalized state $\phi$, $\mu'^B_{\phi}$ is a quantum
probability measure by condition 2. By Gleason's theorem, there is
a mixed state ~$\rho'$, such that $\mu'^B_{\phi}\left(P\right)=\Tr\left(\rho'P\right)=\sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P\right)$
for all event $P$.

Consider the event $P'=\mathbb{1}-\proj{\phi}$, we have 
\begin{eqnarray*}
0 & \overset{\textrm{Condition 3}}{=} & \mu^B_{\phi}\left(P'\right)\\
 & = & \sum_{j=1}^{N}q_{j}\mu^B_{\psi_{j}}\left(P'\right)
\end{eqnarray*}
Because $q_{j}>0$, we have $\mu^B_{\psi_{j}}\left(P\right)=0$,
i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $P'$.
However, the only subspace orthogonal to $P'$ is span by $\ket{\phi}$.
Hence, $\mu'^B_{\phi}=\mu^B_{\phi}$.
\end{proof}

@@

However, there is a $\mathscr{L}_{2}$-valued probability measure
\[
\hat{\mu}_{1}\left(P\right)=\begin{cases}
\imposs & \textrm{, if }P=\proj{+};\\
\bar{\mu}(P) & \textrm{, otherwise.}
\end{cases}
\]
such that $\hat{\mu}_{1}\ne\bar{\mu}_{\psi}$ for all mixed state
$\ket{\psi}$.
